%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.5in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Emery Silberman} % Your name
\address{(+1) 818-388-3258 \\ emerysilb@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	Work Experience
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

%----------------------------------------------------------------------------------------
%	Planted Solar
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Software Engineer}{April 2022 - March 2024}{Planted Solar}{}
\item Spearheaded development of initial solar array layout frontend with Angular on Google Cloud Platform.
\item Solely engineered LiDAR elevation data and slope analysis processing pipeline and backend, solving unique design challenges and providing highly accurate 3D data for project development team.
\item Directed drone and ground GIS surveying and data processing, including managing internal team and procuring and managing third-party consultants.
\item Led integration of serverless architecture allowing quick scale up of users and streamlining computing by ~90\%, reducing runtime for service from 3-5 hours to 15 minutes.
\item Implemented CI/CD tests to existing architecture.
\end{rSubsection}

%----------------------------------------------------------------------------------------
%	Deep Root Technology
%----------------------------------------------------------------------------------------


\begin{rSubsection}{Principal Software Consultant}{November 2020 - April 2022}{Deep Root Technology}{}
    \item Developed multiple publicly available mobile apps for iOS/Android using Flutter with Firebase backend. Projects include H2 Guru, which provides live hydrogen fueling station inventories within the California Fuel Cell Partnership network, and GOES Viewer which provides easy mobile user interface of NOAA satellite imagery. 
    \item Designed an automated system for data collection and processing for soil laboratories using standardized procedures to ensure consistency.
    \item Consulted with tree nursery on tree tracking software and data, including modernizing system and integration with financial backend.

\end{rSubsection}

%----------------------------------------------------------------------------------------
%	Bowles Farm
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Chief Technology Officer}{May 2017 - November 2020}{Bowles Farming Company}{}
    \item Promoted to Chief Technology Officer from Technology Engineer due to a powerful record of performance and exceptional leadership over technology and data processes for a sustainable, tech-driven row crop farm employing over 50 workers. 
    \item Engineered, implemented, and managed new data collection and reporting methods for partners and internal use, including chemical application data, soil moisture, and other key agricultural metrics. This involved managing 30+ iOS devices for data collection in the field.
    \item Pioneered data flow process to integrate financial database with automated reporting to optimize finance department efficiency.
    \item Directed research and implementation of new agricultural technologies to improve workflows efficiencies and business cost-effectiveness.
    \item Developed a training program for technology infrastructure management, translating technical information for a diverse workforce.
    % \item Leveraged drone and satellite imagery/data to optimize crop improvement strategies and decision-making processes.
   \end{rSubsection}

%----------------------------------------------------------------------------------------
%	Sisters of the Valley
%----------------------------------------------------------------------------------------


   \begin{rSubsection}{Web Master and IT Consultant }{February 2016 - April 2017}{Sister of the Valley}{}
    \item Developed WordPress and WooCommerce powered E-Commerce website drawing in over 1,000 visitors per day. 
    \item Led financial database integration for small business with \$1 million in sales annually.
    \item Spearheaded operations system for shipping and tracking packages. 
   \end{rSubsection}

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  Python, Javascript, Typescript, Dart \\
Software \& Tools & React, Angular, Flutter, SQL, Financial BI, Docker , Data Visualization, Data Analytics, Git\\
Infrastructure & GCP, AWS, RESTful API Development,Postgres, CI/CD, Serverless, Microservices Architecture \\
Mapping & Drone Surveying, RTK GPS, Total Station \\
People & Emotional Intelligence, and People Management
\end{tabular}


\end{rSection}
\begin{rSection}{Education}
    \begin{rSubsectionNoItems}{University of California Merced}{}{B.S. Mechanical Engineering}{}
        \end{rSubsectionNoItems}
\end{rSection}
\end{document}